\begin{resumo}[ABSTRACT]
\begin{SingleSpacing}

\imprimirautorcitacao. \imprimirtitleabstract. \imprimirdata. \pageref {LastPage} f. \imprimirprojeto\ – \imprimirprograma, \imprimirinstituicao. \imprimirlocal, \imprimirdata.\\

The migration of Virtual Machines (VMs) is very important when it comes to cloud computing federation enviroments. 
This happens because companies seek to make the best use of the resources available in their infraestructure.
However, managing federation migrations is not a simple task. The management involves a few steps, such as: identifying which VM 
should be migrated, selecting a suitable target, and migration itself.
This work seeks to provide support for the second step, selecting a target for the VM. 
The choice of target hosts may contain different variables, constraints and objectives. 
This paper presents a webservice-based solution that supports migration, with a focus on selecting target hosts for a VM.
As the choice of a destination involves several objectives, the work uses a class of optimization algorithms based on
multiple objetives to find the suitable host. The work also provides a number of constraints
which serve as a filter for hosts that do not meet user-specific business rules.
In addition, it uses known patterns for building the webservice.
The proposed solution has an acceptable performance and is flexible, 
allowing the webservice user to configure the restrictions according to their needs and
select only the objectives of interest.


\textbf{Keywords}: Migration. Multiobjective optimization. REST 

\end{SingleSpacing}
\end{resumo}
